SST_patterns

### 2020-04-06 SST_patterns.Rmd
update

## Using series of general linear hypothese to look for differences in upwelling signal metrics between datasets and between sites
# Is there a significant difference in the duration/intensity etc between the datasets at a particular site

```{r}
load("Data/OISST_final.RData")
load("Data/G1SST_final.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/CMC_final.RData")

combined_products <- rbind(OISST_final,CMC_final,SACTN_upwell_base,MUR_final,G1SST_final)

@@

>>>>

## Using series of general linear hypothese to look for differences in upwelling signal metrics between datasets and between sites (?)
# Is there a significant difference in the duration/intensity etc between the datasets at a particular site

library(tidyverse)
library(multcomp)

load("Data/OISST_final.RData")
load("Data/G1SST_final.RData")
#load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/CMC_final.RData")

combined_products <- rbind(OISST_final,CMC_final,MUR_final,G1SST_final)

@@

metrics <- metric_4years %>% 
  mutate(year = year(date_start)) %>% 
  group_by(product, site) %>% 
  summarise(y = n(),
            mean_intensity = mean(intensity_mean),
            mean_dur = mean(duration),
            mean_cumIn = mean(intensity_cumulative)) %>% 
  rename(count = y)

lmod <- lm(mean_intensity ~ mean_dur, data = metrics)
summary(lmod)

glht(lmod, linfct = K)
